Models of Lambek calculus enriched with subexponentials

### 2019-03-12 PaperDraft.tex
updates

@@

@@

Let us define forcing relation $\Vdash$ between elements of $\mathcal{Q}$ and types as follows for arbitrary valuation map $w : Tp \to \mathcal{A}$:
\begin{enumerate}
  \item Let $p_i \in Tp$, then $\langle a, b \rangle \Vdash p_i \Leftrightarrow \langle a, b \rangle \in w(p_i)$;
  \item $\langle a, b \rangle \Vdash {\bf 1} \Leftrightarrow \langle a, b \rangle \in \mathcal{I}$;
  \item $\langle a, b \rangle \Vdash A \backslash B \Leftrightarrow \forall c \in A, \langle c, a \rangle \Vdash A \Rightarrow \langle c, b \rangle \Vdash A$;
  \item $\langle a, b \rangle \Vdash B / A \Leftrightarrow \forall c \in A, \langle a, c \rangle \Vdash A \Rightarrow \langle b, c \rangle \Vdash A$;
  \item $\langle a, b \rangle \Vdash A \bullet B \Leftrightarrow \exists c, \langle a, c \rangle \Vdash A \text{ and } \langle c, b \rangle \Vdash B$;
  \item $\langle a, b \rangle \Vdash A \lor B \Leftrightarrow \langle a, b \rangle \Vdash A \text{ or } \langle a, b \rangle \Vdash B$;
  \item $\langle a, b \rangle \Vdash A \& B \Leftrightarrow \langle a, b \rangle \Vdash A \text{ and } \langle a, b \rangle \Vdash B$;
  \item $\langle a, b \rangle \Vdash !A \Leftrightarrow \exists S_{\langle a, b \rangle} \forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \Vdash A$
  \item $\langle a, b \rangle \Vdash \Gamma \rightarrow A \Leftrightarrow \langle a,b \rangle \Vdash A_1 \bullet \dots \bullet A_n \Rightarrow  \langle a,b \rangle \vdash A$;
\end{enumerate}

Example:

\begin{itemize}
Let us show that $\mathcal{Q} \models !A \rightarrow A$.

Let $\mathcal{Q} \models !A$ and $v$ be a valuation, hence $\langle a, b \rangle \Vdash !A$.
Hence there exists $S_{\langle a, b \rangle} \subseteq \mathcal{Q}$,
such that $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models A$,
but $\langle a, b \rangle \in S_{\langle a, b \rangle}$, so $\langle a, b \rangle \models A$.

\item Let us show that $\mathcal{Q} \models !A \rightarrow !!A$.

Let $\langle a, b \rangle \models !A$. Let us show that $\langle a, b \rangle \models !!A$.

So there exists $S_{\langle a, b \rangle} \subseteq \mathcal{Q}$,
such that $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models A$.

Let $S' \subseteq S_{\langle a, b \rangle}$, then for each $\langle a', b' \rangle \in S', \langle a', b' \rangle \Vdash A$,
so $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models !A$, so  $\langle a, b \rangle \models !!A$.
\end{itemize}

\begin{theorem}

  Let $\langle A \rangle$
\end{theorem}

  Let $\mathcal{Q}$ be a relational quantale, then $Log(\mathcal{Q}) = L^{*}(\backslash, /, \bullet, {\bf 1}, \&, \vee)$.
\end{theorem}

>>>>

\begin{comment}

@@

\end{comment}

@@

\begin{theorem}
  Every unital quantale $\mathcal{Q} = \langle A, \leq, \cdot, \bigvee \rangle$ with quantic conucleus $\Box$ is
  isomorphic to some relation quantale $\hat{\Box}$
\end{theorem}

\begin{proof}
  Consider a relational quantale by Brown and Gurr $\hat{\mathcal{Q}} = \langle \mathcal{R}, \subseteq, \circ, \bigvee \rangle$ where:
  \begin{enumerate}
    \item $\hat{a} = \{ \langle b, c \rangle \: | \: b \cdot a \leq c \}$;
    \item $\widehat{a \cdot b} = \hat{a} \circ \hat{b}$;
    \item $\widehat{\bigvee a} = \bigvee \hat{a}$.
  \end{enumerate}

  Consider $\hat{\Box} \hat{a} = \bigvee $

  \begin{enumerate}
    \item $\hat{\Box} \hat{a} \subseteq \hat{a}$;
    \item $\hat{\Box} \hat{a} \subseteq \hat{\Box} \hat{\Box} \hat{a}$;
    \item $\hat{a} \subseteq \hat{b} \Rightarrow \hat{\Box}\hat{a} \subseteq \hat{\Box}\hat{b}$;
    \item $\hat{\Box}\hat{a} \circ \hat{\Box}\hat{b} \subseteq \Box(\hat{a} \circ \hat{b})$;
    \item $\hat{\Box}\hat{\varepsilon} = \hat{\varepsilon}$.
  \end{enumerate}

  Let us show that $\hat{\Box} \hat {a} = \widehat{\Box a} = \{ \langle b, c \rangle \: | \:  b \cdot \Box a \leq c \}$
\end{proof}

\begin{defin}
  Let $W$ be a set. A Kripke frame is a pair $\mathcal{W} = \langle W, R, I \rangle$,
  where $R$ is a ternary relation on $W$ and $I$ is an unary relation on $W$.

  A Kripke model is a triple $\mathcal{M} = \langle \mathcal{W}, v \rangle$, where
  $\mathcal{W}$ is a Kripke frame and $v : Tp \to 2^W$.

  A forcing relation is defined as follows:

  \begin{enumerate}
    \item $\mathcal{W}, w \Vdash p_i \Leftrightarrow w \in v(p_i)$;
    \item $\mathcal{W}, w \Vdash {\bf 1} \Leftrightarrow I(w)$;
    \item $\mathcal{W}, w \Vdash A \bullet B \Leftrightarrow \exists u, v \in W, R(u,v,w) \text{ and } \mathcal{W}, u \Vdash A \text{ and } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{W}, w \Vdash A \backslash B \Leftrightarrow \forall u, v \in W, R(u,w,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{W}, w \Vdash B / A \Leftrightarrow \forall u, v \in W, R(w,u,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{W}, w \Vdash A \lor B \Leftrightarrow \forall u, v \in W, R(u,v,w) \text{ either } \mathcal{W}, u \Vdash A \text{ or } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{W}, w \Vdash A \land B \Leftrightarrow \mathcal{W}, w \Vdash A \text{ and } \mathcal{W}, w \Vdash A$;
    \item $\mathcal{W}, w \Vdash \Gamma \rightarrow A \Leftrightarrow \mathcal{W}, w \Vdash \bullet \Gamma \text{ implies } \mathcal{W}, w \Vdash A$.
  \end{enumerate}
\end{defin}

\begin{theorem} Soundness
$ $

  Let $\mathbb{F}$ be a class of Kripke frames, then $Log(\mathbb{F}) = L^{*}_{\bf 1} \land \lor$.
\end{theorem}

  \begin{enumerate}
  \item Let $\Gamma \rightarrow A$. By IH, for each $\mathcal{W}, w \Vdash \Gamma \rightarrow A$.
  \item Let $\Gamma, A, \Delta \rightarrow C$ and $\Gamma, B, \Delta \rightarrow C$,
  \item Let $\Gamma \rightarrow A$ and $\Gamma \rightarrow B$
  \item Let $\Gamma \rightarrow A_1 \land A_2$, so $\mathcal{W}, w \Vdash \Gamma \rightarrow A_i$, $i = 1,2$.
  \end{enumerate}
\end{proof}

\begin{theorem} Strong completeness
$ $

  $\Gamma \models A$ implies that $L^{*}_{\bf 1} \land \lor \vdash \Gamma \rightarrow A$
\end{theorem}

\begin{defin}
  By ${L^{*}_{\bf 1} \land \lor}_{\bf S4}$ we mean $SMALC_{\Sigma}$, where $\Sigma = \{ s \}$ and $C = W = E = \emptyset$.
\end{defin}
